---
title: Colophon
freeze: false
format:
  html:
    include-in-header:
      - text: |
          <style>
            .font-example {
                background: #ffffff;
                padding: 1.5em 1.5em 0.75em 1.5em;
                margin-bottom: 1rem;
                border-left: 10px solid #ffcc3d;
                border-top: 1px solid #ffcc3d;
                border-right: 1px solid #ffcc3d;
                border-bottom: 1px solid #ffcc3d;
                font-size: 0.95em;
            }

            .fake-heading {
                font-family: "Alan Sans";
                font-weight: 700;
                font-size: 1.3em;
            }
          </style>
    knitr:
      opts_chunk:
        dev-args:
          bg: "transparent"
---

```{r}
#| label: packages-functions
#| include: false

library(tidyverse)
library(scales)

show_nice_pal <- function(pal, nrow = 1, show_text = TRUE) {
  out <- tibble(x = 1:length(pal), color = pal) |>
    mutate(color = fct_inorder(color)) |>
    ggplot(aes(x = color, y = 1, fill = color)) +
    geom_tile() +
    scale_x_discrete(expand = c(0, 0)) +
    scale_fill_identity() +
    facet_wrap(vars(x), scales = "free_x", nrow = nrow) +
    theme_void(base_family = "Inconsolata") +
    theme(
      panel.spacing.x = unit(-1, units = "pt"),
      panel.spacing.y = unit(-0.5, units = "lines"),
      strip.text = element_blank()
    )

  if (show_text) {
    out <- out +
      theme(
        axis.text.x = element_text(margin = margin(b = 5)),
        panel.spacing.y = unit(0, units = "lines")
      )
  }

  return(out)
}

time_updated <- format(
  lubridate::now(tzone = "America/New_York"),
  "%F at %T US Eastern"
)
```

## Technology

- **Last built**: `{r} time_updated`
- **Software**: Quarto version {{< version >}} and {{< fa brands r-project >}} `{r} R.version$version.string`
- **Hosting**: Hosted at [{{< fa brands github >}} GitHub Pages](https://andrewheiss.github.io/quarto-websites_2025-10/) and built and deployed using [{{< fa brands github >}} GitHub Actions](https://github.com/andrewheiss/quarto-websites_2025-10/blob/main/.github/workflows/publish.yml)


## Design

The typography, colors, and custom CSS settings are all controlled with [this `_brand.yml` file](https://github.com/andrewheiss/quarto-websites_2025-10/blob/main/_brand.yml):

<details>
<summary>Show `_brand.yml` for this site</summary>

```{.yaml filename="_brand.yml"}
{{< include _brand.yml >}}
```

</details>

[(See more about brand.yml [here](https://posit-dev.github.io/brand-yml/)).]{.small}


### Typefaces

I use [Open Sans](https://en.wikipedia.org/wiki/Open_Sans) [([Google Fonts](https://fonts.google.com/specimen/Open+Sans))]{.small} as the main body font throughout the site, and I use [Alan Sans](https://github.com/alan-eu/Alan-Sans){style="font-family: 'Alan Sans'"} [([Google Fonts](https://fonts.google.com/specimen/Alan+Sans))]{.small} for all headings.

::: {.font-example}
[A heading]{.fake-heading}

Whereas recognition of the *inherent dignity* and of the ***equal and inalienable*** rights of all members of the human family is the foundation of freedom, justice and peace in the world…
:::

### Colors

The colors for this course website come primarily from the ["ustwo" palette](https://github.com/BlakeRMills/MoMAColors?tab=readme-ov-file#ustwo) from [the {MoMAColors} R package](https://github.com/BlakeRMills/MoMAColors). The colors come from the video game [Monument Valley](https://www.monumentvalleygame.com/mv1), developed and produced by [ustwo](https://ustwo.com/), and is one of only a few pieces of software-based art in the MoMA [([see its MoMA page](https://www.moma.org/collection/works/409699?classifications=3&date_begin=Pre-1850&date_end=2023&direction=fwd&page=3&q=&utf8=%E2%9C%93&with_images=1))]{.small}.

::: {.column-margin}
![Monument Valley, 2014, ustwo, video game software, [MoMA link](https://www.moma.org/collection/works/409699?classifications=3&date_begin=Pre-1850&date_end=2023&direction=fwd&page=3&q=&utf8=%E2%9C%93&with_images=1).](img/monument-valley.jpg){width="80%" fig-align="left"}
:::

```{r}
#| label: show-ustwo
#| fig-width: 8
#| fig-height: 1
#| out-width: 100%
#| echo: false

MoMAColors::moma.colors("ustwo") |> 
  show_nice_pal(show_text = TRUE, nrow = 1)
```

Since this palette only has 6 colors, I supplement it with a few colors from the [qualitative Prism palette from CARTOColors](https://carto.com/carto-colors/):

```{r}
#| label: show-prism
#| fig-width: 6
#| fig-height: 1
#| out-width: 75%
#| echo: false

rcartocolor::carto_pal(name = "Prism")[c(1, 3, 4, 11)] |> 
  show_nice_pal(show_text = TRUE, nrow = 1)
```


## License and credits

All the materials and content for this course are licensed under [{{< fa brands creative-commons >}} Creative Commons CC-BY-SA {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}}](https://github.com/posit-conf-2025/quarto-brand/blob/main/LICENSE.md).

Some of the materials in the course were adapted from Isabella Velásquez and Sara Altman's [posit::conf(2025) workshop](https://posit-conf-2025.github.io/quarto-brand/) on branded Quarto documents ([{{< fa brands github >}} GitHub repository](https://github.com/posit-conf-2025/quarto-brand)). They graciously licensed their content under [{{< fa brands creative-commons >}} Creative Commons CC-BY-SA {{< fa brands creative-commons-by >}} {{< fa brands creative-commons-sa >}}](https://github.com/posit-conf-2025/quarto-brand/blob/main/LICENSE.md).
